Generative AI for Image Reconstruction with Intensity Interferometry: A First Attempt

### 2024-10-16 Phase_II/draft/main.tex
..

\begin{abstract}
In modern astronomy, the simulation of Intensity Interferometry demonstrates significant advancements in the high-precision resolution of stellar objects at optical wavelengths. Despite these achievements, phase retrieval of the signal remains challenging due to photon correlation, hence the image reconstruction. Nowadays, artificial intelligence (AI) techniques are at the forefront of revealing astronomical mysteries by analyzing observed data. This paper proposes the application of a conditional Generative Adversarial Network (cGAN) to Intensity Interferometry data for high-resolution optical astronomy, aiming to overcome the limitations of traditional image reconstruction methods. Here, the cGAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star. Simulations of II are based on an assembly of four telescopes similar to existing arrays. However, the sensitivity of the signal and high resolution are expected to improve with additional baselines, which makes the current and future Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for II applications. This approach is highly relevant and innovative, addressing key challenges in phase reconstruction and proposing novel solutions that could revolutionize high-resolution imaging in astronomy.	
\end{abstract}
\input{intro}
\input{II}
\input{GAN}
\input{ParaGan}
\input{Result}
\input{conclusion}

>>>>

\begin{abstract}
In modern astronomy, simulation and observation with Intensity Interferometry (II) are showing noteworthy progress with optical wavelengths to achieve high-resolved stellar objects. Despite these achievements, phase retrieval of the signal remains challenging due to photon correlation, hence the image reconstruction. Here, we propose the application of a conditional Generative Adversarial Network (cGAN) to II simulated data to overcome the limitations of traditional image reconstruction methods, as Artificial Intelligence (AI) techniques are at the forefront of revealing astronomical mysteries by analyzing the signal. Here, the cGAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star. Simulations of II are based on an assembly of four telescopes similar to existing arrays. However, the sensitivity of the signal and high resolution are expected to improve with additional baselines, which makes the current and future Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for II applications. This approach is highly relevant to the existing image reconstruction technique with II and could revolutionize high-resolution imaging in astronomy.
\end{abstract}
\input{intro}
\input{II}
\input{GAN}
\input{ParaGan}
\input{Result}
\input{conclusion}
